Co-citations in context

### 2019-06-14 cocit_r.tex
very minor edits

Averaging the result of 1,000 simulations for each dataset studied, z-scores were then calculated for each journal-pair using the formula $(F_{obs} - F_{exp})/\sigma$ where $F_{obs}$ is the observed frequency, $F_{exp}$ is the averaged simulated frequency, and $\sigma$ is the standard deviation of the simulated frequencies for a journal pair. As a result of these calculations, each publication becomes associated with a set of z-scores corresponding to the journal pairs derived from pairwise combinations of its cited references. Positional statistics of z-scores were calculated for each publication, which was then labeled according to conventionality and novelty: (i) HC if the median z-score exceeded the median of median z-scores for all publications and LC otherwise
%if the median z-score was equal to or less than the median of median z-scores for all publications
, and (ii) HN if the tenth percentile of z-scores for a publication was less than zero, and LN otherwise. 
%if the tenth percentile of z-scores for a publication was greater than zero. 
We also analyzed the effect of defining high novelty using the first percentile of z-scores.

>>>>

Averaging the result of 1,000 simulations for each dataset studied, z-scores were then calculated for each journal-pair using the formula $(F_{obs} - F_{exp})/\sigma$ where $F_{obs}$ is the observed frequency, $F_{exp}$ is the averaged simulated frequency, and $\sigma$ is the standard deviation of the simulated frequencies for a journal pair. As a result of these calculations, each publication becomes associated with a set of z-scores corresponding to the journal pairs derived from pairwise combinations of its cited references. Positional statistics of z-scores were calculated for each publication, which was then labeled according to conventionality and novelty: (i) HC if the median z-score exceeded the median of median z-scores for all publications and LC otherwise and
%if the median z-score was equal to or less than the median of median z-scores for all publications and
(ii) HN if the tenth percentile of z-scores for a publication was less than zero and LN otherwise. 
%if the tenth percentile of z-scores for a publication was greater than zero. 
We also analyzed the effect of defining high novelty using the first percentile of z-scores.
